Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-15 trunk/papers/icsoc2010/paper_sec_use_case.tex
new architecture picture
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@880 d8b0c59b-6544-0410-94d9-83a5658a058e

The intention of this paper was to show the advances made regarding web service discovery and consumption through the two artifacts developed as part of our research. While these artifacts may be deployed and used separately by third-party applications, they were originally developed to form the backbone of the FAST platform.
FAST constitutes a novel approach to application composition and business process definition from a top-down user-centric perspective. Therefore, it is aimed at allowing users (mainly business users at the management level, without programming experience) to create their own situational applications by visually combining different components, or building blocks, such as graphical forms and back-end services in terms of their inputs and outputs. These two components, as described in Sects. 3 and 4, are fully integrated and present a high cohesion with the rest of the components of the FAST architecture (see Fig.~\ref{fig:fast_architecture}).

\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=.9\linewidth]{images/fast_architecture.png}
    \caption{Overview of the FAST architecture}
    \label{fig:fast_architecture}
  \end{center}
\end{figure}

@@

The publishing platform presented, called ``Metadata Catalogue'' within the FAST platform, covers several important purposes:
\begin{description}
	\item[Publication and search of gadgets] The output of the FAST IDE are gadgets, which are self-contained and ready to use. They need to be made available for download, as well as being discovered according to their formal description.
	\item[Publication and search of building blocks] Every single component or building block definition is stored in the catalogue, which facilitates searching, recommendation and planning (the suggestion of combinations of building blocks to fulfil certain requirements). 
	\item[Storage and indexing of user profiles and histories] Each user of the FAST platform has a representation in the catalogue, thus making it possible for the IDE to make informed guesses about what they want in a particular situation, based on their previous behaviour.
	\item[Facilitate ontology mediation] Because FAST allows the integration of third-party external services, it is not always guaranteed that all the data coming from a service is directly compatible with the FAST platform. In such cases, mediation between the different ontologies is necessary. The catalogue provide some grade of mediation functionality (which is not covered in this paper).
\end{description}

>>>>

The intention of this paper was to show the advances made regarding web service discovery and consumption through the two artifacts developed as part of our research. While these artifacts may be deployed and used separately by third-party applications, they were originally developed to form the backbone of the FAST platform.
FAST constitutes a novel approach to application composition and business process definition from a top-down user-centric perspective. Therefore, it is aimed at allowing users (mainly business users at the management level, without programming experience) to create their own situational applications by visually combining different components, or building blocks, such as graphical forms and back-end services in terms of their inputs and outputs. The work covered in this paper are the components highlighted and surronded by a dashed frame in the Fig.~\ref{fig:fast_architecture}. These components have public interfaces to communicate with any application developed by a third-party developer or company, and as described in Sects. 3 and 4, are fully integrated and present a high cohesion with the rest of the components of the FAST architecture.

\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=.9\linewidth]{images/fast_architecture.pdf}
    \caption{Overview of the FAST architecture}
    \label{fig:fast_architecture}
  \end{center}
\end{figure}

@@

The publishing platform presented, also called ``Catalogue'' within the FAST platform, covers several important purposes:
\begin{description}
	\item[Publication and search of gadgets] The output of the FAST IDE are gadgets, which are self-contained and ready to use. They need to be made available for download, as well as being discovered according to their formal description.
	\item[Publication and search of building blocks] Every single component or building block definition is stored in the catalogue, which facilitates searching, recommendation and planning (the suggestion of combinations of building blocks to fulfil certain requirements). 
	\item[Storage and indexing of user profiles and histories] Each user of the FAST platform has a representation in the catalogue, thus making it possible for the IDE to make informed guesses about what they want in a particular situation, based on their previous behaviour.
	\item[Facilitate ontology mediation] Because FAST allows the integration of third-party external services, it is not always guaranteed that all the data coming from a service is directly compatible with the FAST platform. In such cases, mediation between the different ontologies is necessary. The catalogue provide some grade of mediation functionality (which is not covered in this paper).
\end{description}
